%--------------------------- Introduction ----------------------------------------------------------------------- 
\section{Introduction}
\subsection{Purpose}

This document defines the mission, goals and objectives, organization and responsibilities of Vera C. Rubin Observatory System Performance Department.

\subsection{Mission Statement}

Rubin Observatory System Performance department is responsible for ensuring that the Legacy Survey of Space and Time (LSST) as a whole is proceeding with the efficiency and fidelity needed to achieve its science requirements at the end of the 10-year survey. 
This includes the Wide-Fast-Deep (WFD) survey and all Special Programs (deep drilling fields, Target of Opportunity (ToO) and mini/micro/nano surveys)


\subsection{Goals and Objectives}

{\emph Track  and optimise} the performance of the entire system including the observatory performance and survey progress with respect to the science objectives, and the evaluation of strategies for improving the survey strategy;

{\emph Provide QA and performance characterization analyses}  of the data products, understand and minimize systematics, gather user feedback – all as input  to the Data Release board to assess Rubin’s schedule to make annual data releases;

\emph{Enable the community to access and analyze the data} and publish results on the four LSST science pillars at an appropriate rate.

\emph{Oversight and implementation of Change and Process control} through a Change Control Board (CCB), and Risk and Opportunity Management, both chaired by the Lead Systems Engineer.

%------------------------Lifecycle of the Data--------------------------------------------------------------------------
\section{Approach -- Lifecycle of the Data} 

System Performance adopts a lifecycle of the data approach to its work. 


%-------------------------Processes and Tools-------------------------------------------------------------------------
\section{Processes and tools}


%------------------------Teams and Organization--------------------------------------------------------------------------
\section{Team and Organization}

System Performance comprises four functional teams. 

\input{validation}
\input{community}
\input{survey}
\input{syseng}
%-------------------------Roles and Responsibilities -------------------------------------------------------------------------
\section{Roles and Responsibilities}

% Extract a table from the WBS of all roles and responsibilities 

This section details the roles and responsibilities in System Performance. 
They come from the WBS 

%-------------------------Communications -------------------------------------------------------------------------
\section{Communications}

This section covers intra-department communications and 
Slack and email are used. 
High-level slack channels are used for prompt communications 

AHM once per year

%------------------------Product Tree --------------------------------------------------------------------------
\section{Product Tree }

This section details the System Performance products and product tree . 

Products include 1) Software, 2) Data Products and Documentation 3) Services, 
